Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
editing

All experiments were conducted on a 12-core 2.40\,GHz Intel Xeon E5-2440 with 96\,GB
of RAM, and Linux OS.  All times given are wall clock time in seconds as measured
by the UNIX date command.  For the inductive back-end, we apply a timeout of 8 hours
per benchmark, and 24 hours for the interval arithmetic back-end.

@@

\vspace{0.5em}
\scriptsize{* = solved with interval back-end, $\dagger$ = with uncertainty}
\vspace{0.5em}

>>>>

All experiments were conducted on a 12-core 2.40\,GHz Intel Xeon E5-2440 with 96\,GB
of RAM, and Linux OS.  All times given are wall clock time in seconds as measured
by the UNIX date command.  For the approach using a two-stage verification engine
we apply a timeout of 8 hours
per benchmark, and 24 hours for the approach using a one-stage engine.

@@

\vspace{0.5em}
\scriptsize{* = solved with the one-stage engine, $\dagger$ = with uncertainty}
\vspace{0.5em}
